Experiments

### 2020-10-23 StateOfPractice/Methodology/Experiments.tex
added comments into Experiments file regarding modifiability experiment

~\newpage
\section{Modifiability Experiments}
copied from Methodology:

\pmi{note: these experiments need to be completed - to be discussed at next meeting}\pmi{meeting: start thinking about maintainability experiments; maybe change to modifiability; at least describe what we would do for such experiments - measure sensible changes, what does a small change mean exactly, document 'likely changes' - see Parnas; modifiability - we want to be explicit about what we want to modify; how to we interpret the results?; Add these experiments to user experiments file, in such case change file name, keep format similar to user experiments (procedure, no questionnaire, add preamble describing comments above), such experiments would get quantitative measures}\pmi{SS:For the maintainability experiment, I think we should write it up in the methodology, even if we don't do it. Discussing maintainability is needed to fit with the research questions (since maintainability is part of sustainability). We want sustainability to fit into the bigger context of what interests research software developers. As far as the maintainability experiment goes, we can just ask the domain experts to make a likely change and ask them to record their experience with making the change. It isn't quantifiable, but it would give us qualitative data.}
\subsection {Procedure}

>>>>

~\newpage
\section{Modifiability Experiments}
\pmi{add preamble here describing some of the notes below}

What can be done to measure modifiability?

Idea: measure sensible changes

Can we measure sensible changes? How?

We could gather qualitative data about the process of attempting to make sensible changes. Perceived difficulty, available documentation, prerequisite knowledge, time/effort required, tools required, errors and issues encountered and ability to overcome those issues with the available resources, is there dev support? How to interpret results?

What does a small change mean? What are likely changes - See Parnas

Parnas identifies likely changes as:

 Likely Changes: if the system is required to be easy to change, the requirements should  contain  a  definition  of  the  areas  that  are  considered  likely  to  change.  You  cannot design a system so that everything is equally easy to change. Programmers should not have to decide which changes are most likely\cite{parnas1986rational}

We want to be explicit about what we want to modify.

\subsection {Procedure}
\begin{enumerate}
	\item Identify likely changes using procedure x
	\item Select from likely change list (using what criteria)
	\item Gather relevant documentation?
	\item Ask the domain expert to make the (selected) likely change(s)
	\item Have the domain expert answer a questionnaire about their attempt to make the likely change
\end{enumerate}
